%-------------------------
% Resume Template
% Author : Ruchita Das
%------------------------

%-------------------------------------------------------------------------------
%                Document & Class
%-------------------------------------------------------------------------------

\documentclass[letterpaper]{resume_config}

% NOTE: <- font size adjustment is available in the resume_config.cls file on the left hand side. ex. \LoadClass[#pt]{article} where # is 10, 11 or 12

% NOTE: If you need to adjust the space between any two lines, use this function: \vspace{#pt} where # is your number. ex. \vspace{-5pt} decreases the space between lines

%-------------------------------------------------------------------------------
%                Resume Starts Here
%-------------------------------------------------------------------------------

\begin{document}

\Header
    {Ruchita Das} % name
    {(+91)xxxxx-xxxxx} % phone number
    {ruchita.das01@gmail.com} % email
    {ruchitadas3938} % https://linkedin.com/in/ruchita3938
    {ruchita98} % https://github.com/ruchita98
\
%-------------------------------------------------------------------------------

%                Education
%-------------------------------------------------------------------------------

\section{Education}

\EducationExperience
    {IIT Kharagpur} % school name
    {Bachelors and Masters (Dual Degree) in Mathematics and Computing (CGPA: $8.23/ 10$)} % credential name
    {2015 - 2020} % date of graduation
    {Kharagpur, India} % city, country of school
    {Micro specialization in Optimization Theory \& Applications}

\vspace{-10pt}
%-------------------------------------------------------------------------------

%                Work Experience
%-------------------------------------------------------------------------------

\section{Work Experience}

\WorkExperience
    {Full stack iOS Developer} % job title
    {Microsoft} % company name
    {April 2022 -- present} % beginning and end of employment. If currently employed write " - Present"
    {Hyderabad, India} % city, country of employment
    {MD mobile service}
    {
        \item Implemented key Defender security features, including Threat Vulnerability Management and Malicious Certificates \& Profiles Detection. 
    }
    {
        \item Designed and implemented scalable microservices architecture to host web APIs, ensuring high availability.
        \item Developed cron jobs and web jobs to automate the fetching and processing of installed apps, certificates \& profiles data from MDM-enrolled iOS devices.
        \item Successfully supported approximately \textbf{$1$ million } active devices of \textbf{$5,000$} tenants distributed across multiple geos.
    }

\vspace{5pt}
\WorkExperience
    {iOS Developer} % job title
    {Microsoft} % company name
    {July 2020 -- March 2022} % city, country of employment
    {Hyderabad, India} % beginning and end of employment. If currently employed write " - Present"
    {Microsoft Defender for iOS}
    {
        \item Led the development of key features of MDE iOS app. Streamlined the user interface and enhanced app functionality, resulting in a $20\%$ increase in user engagement, earning an \textbf{'On the Spot Award'} for demonstrating exceptional customer obsession and setting new standards for user experience.
        \item Integrated the enterprise Defender app with the consumer backend service to enhance the consumer offering with family device management capabilities.
    }
    {
        \item Successfully enabled management features for family devices, catering to a user base of $100,000$ active devices.
    }

\vspace{5pt}
\WorkExperience
    {Summer Analyst} % company name
    {Goldman Sachs} % job title
    {May 2019 -- July 2019} % city, country of employment
    {Bangalore, India} % beginning and end of employment. If currently employed write " - Present"
    {Franchise Analytics, Strategy and Technology (FAST) Division: Securities}
    {
        \item Developed a framework for Knowledge based Dynamic Dashboard which helps user to input queries in a specified text format to get the output in tabular form.
    }
    {
        \item Designed a configurable structure that accesses input datasets and questions to create instant dashboards.
        \item Identified patterns in key business questions asked by the users. Structured the questions into series of filter-aggregation.
        \item Developed a rule-based parser that can identify all filters, aggregations and their correct order from user query.
        \item Converted the text into structured text and built a system to generate SQL queries.
        }


\section{Projects}
\Project
    {Stochastic Systems Lab, Dept. of CSA | IISc. Bangalore | Prof. Shalabh Bhatnagar}
    {May '18 - July '18}
    {
        \item Worked in a \textit{research project} on \textbf{Vehicular Path Planning Problem}. The objective was to find optimal way of choosing a path to minimize average waiting time of all vehicles in the network.
    }
    {
        \item Designed a novel approach of modelling the traffic as Markov decision process. Defined congestion tuple of roads as a state vector. Computed aggregated waiting time of vehicles between state transitions as a cost to minimize. Deployed a Q-learning system that resulted in reducing average delay compared to baseline, static routing policy.
    }
    {Reinforcement Learning | Sumo Simulator | TraCI (Traffic Control Interface)}

\vspace{5pt}

\Project
    {Vinod Gupta School of Management (VGSoM) | IIT Kharagpur | Prof. Swagato Chatterjee}
    {Feb '20 - May '20}
    {
        \item Extracted useful specifications of a domain specific B2B (Business-to-Business) software from its customer reviews using topic modeling approach. 
    }
    {
        \item Utilized a dataset consisting of full review texts of various 'Customer Relationship Management' (CRM) softwares from more than $5,000$ users. First baseline (LSA, LDA) models were built and then optimal models were deployed that produced the highest coherence value. Also, distributions of topics, important keywords and total number of review-text associated with each topic were calculated to assess the strength of our model.
    }
    {Web scraping | Beautifulsoup | Exploratory Data Analysis | Topic Modeling}

\section{Skills}

\vspace{1pt}

\SkillList{
    \SkillItem{Languages}{: Swift, Objective-C, C Sharp, C++, Python}
    \SkillItem{Tools and Frameworks}{: UIKit, SwiftUI, Dotnet, Docker, AzureSQL, OpenCV, AutoCAD, SolidWork, LaTeX}
}

\vspace{-2pt}
\end{document}

%-------------------------------------------------------------------------------
%                Resume Ends Here
%-------------------------------------------------------------------------------
